FIN 416 Tables

### 2025-03-20 416 Tables, Nearly done.qmd
Added Updated Files

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(tidyr)
library(tidyselect)
library(stats)
library(PerformanceAnalytics)
library(xts)
library(gt)
library(RTL)
library(plotly)
library(ggplot2)
library(arrow)
library(patchwork)
library(tidyquant)
library(scales)
#library(ggridges)
#library(viridis)
library(forcats)
library(scales)
library(lubridate)
library(stats)
library(broom)
library(gt)
#library(car)
library(GGally)
library(rlang)
library(glue)
library(purrr)
library(ggfortify)
library(ggpmisc)

@@

port_returns_annualized <- port_returns_wide %>%
  mutate(across(all_of(return_columns), ~ (1 + .)^12 - 1))

@@

summary_table_14 %>% gt()

@@

# Slide 17 New vs Base Long
```{r echo=FALSE}

@@

summary_table_17 %>% gt()

@@

# Slide 17 Visual
```{r echo=FALSE}

@@

summary_table_18 %>% gt()

@@

# Slide 18 Visual
```{r echo=FALSE}

@@

```
# Slide 21 Table (Im Confused)
```{r echo=FALSE}
slide21_data <- port_returns_annualized %>% 
  select(DATE,RET_LongPosV1,RET_LongPosV2,RET_ShortPosV1,RET_ShortPosV2) %>% 
  mutate(
    BaseLong = RET_LongPosV1,
    BaseShort = RET_ShortPosV1,
    NewLong = RET_LongPosV2,
    NewShort = RET_ShortPosV2
             )

slide21_table <- slide21_data %>% 
  summarise(
    across(c(BaseLong, BaseShort, NewLong, NewShort), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Min = ~ min(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE))))

summary_table_21 <- slide21_table %>%
  pivot_longer(everything(), names_to = c("Column", "Metric"), names_sep = "_", values_to = "Value") %>%
  pivot_wider(names_from = Column, values_from = Value)

summary_table_21 %>% gt()
```

>>>>

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
library(tidyverse)
library(tidyr)
library(tidyselect)
library(stats)
library(PerformanceAnalytics)
library(xts)
library(gt)
library(RTL)
library(plotly)
library(ggplot2)
library(arrow)
library(patchwork)
library(tidyquant)
library(scales)
library(ggridges)
library(viridis)
library(forcats)
library(scales)
library(lubridate)
library(stats)
library(broom)
library(gt)
library(car)
library(GGally)
library(rlang)
library(glue)
library(purrr)
library(ggfortify)
library(ggpmisc)
library(devtools)

@@

port_returns_annualized <- port_returns_wide

@@

summary_table_14 %>% 
   gt() %>% 
  fmt_percent(
    columns = where(is.numeric), # Apply only to numeric columns
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), # Filter only Mean, StDev, and Max
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 # Adjust to desired decimal places
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 # Adjust to desired decimal places
  )

@@

# Slide 17 New vs Base Long

@@

summary_table_17 %>% 
  gt() %>% 
  fmt_percent(
    columns = where(is.numeric), 
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), 
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 
  )

@@

# Slide 17 Visual

@@

summary_table_18 %>% 
  gt() %>% 
  fmt_percent(
    columns = where(is.numeric), 
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), 
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 
  )

@@

# Slide 18 Visual

@@

# Slide 21 Table (Im Confused)

```{r echo=FALSE}
slide21_data_IVOL <- port_df_wide %>%
  select(DATE, IVOL_LongPosV1, IVOL_LongPosV2, IVOL_ShortPosV1, IVOL_ShortPosV2) %>%
  mutate(Year = year(DATE), Month = month(DATE)) %>%  
  filter(Month == 12) %>%  
  group_by(Year) %>% 
  slice_tail(n = 1) %>%  #
  ungroup()

slide21_summary_table <- slide21_data_IVOL %>%
  select(IVOL_LongPosV1,IVOL_LongPosV2, IVOL_ShortPosV1, IVOL_ShortPosV2) %>% 
  rename_with(~ str_remove(.x, "IVOL_"), starts_with("IVOL_")) %>% 
  summarise(
    across(
      c(LongPosV1, LongPosV2, ShortPosV1, ShortPosV2), 
      list(
        Mean = ~ mean(.x, na.rm = TRUE),
        StDev = ~ sd(.x, na.rm = TRUE),
        Max = ~ max(.x, na.rm = TRUE),
        Min = ~ min(.x, na.rm = TRUE)
      )
    )
  ) %>%
  pivot_longer(
    cols = everything(), 
    names_to = c("Column", "Metric"), 
    names_sep = "_", 
    values_to = "Value"
  ) %>%
  pivot_wider(
    names_from = Column, 
    values_from = Value
  )

slide21_summary_table %>%
  gt() %>%
  fmt_number(
    columns = where(is.numeric), 
    decimals = 2 
  )
```

```{r echo=FALSE}
slide21_data_SKEW <- port_df_wide %>%
  select(DATE, SKEW_LongPosV1,SKEW_LongPosV2,SKEW_ShortPosV1,SKEW_ShortPosV2) %>%
  mutate(Year = year(DATE), Month = month(DATE)) %>%  
  filter(Month == 12) %>%  
  group_by(Year) %>% 
  slice_tail(n = 1) %>%  
  ungroup()

slide21_summary_table_SKEW <- slide21_data_SKEW %>% 
  select(SKEW_LongPosV1,SKEW_LongPosV2,SKEW_ShortPosV1,SKEW_ShortPosV2) %>% 
  rename_with(~ str_remove(.x, "SKEW_"), starts_with("SKEW_")) %>% 
  summarise(
    across(
      c(LongPosV1, LongPosV2, ShortPosV1, ShortPosV2), 
      list(
        Mean = ~ mean(.x, na.rm = TRUE),
        StDev = ~ sd(.x, na.rm = TRUE),
        Max = ~ max(.x, na.rm = TRUE),
        Min = ~ min(.x, na.rm = TRUE)
      )
    )
  ) %>%
  pivot_longer(
    cols = everything(), 
    names_to = c("Column", "Metric"), 
    names_sep = "_", 
    values_to = "Value"
  ) %>%
  pivot_wider(
    names_from = Column, 
    values_from = Value
  )

slide21_summary_table_SKEW %>%
  gt() %>%
  fmt_number(
    columns = where(is.numeric), 
    decimals = 2 
  )
```

# Slide 23

symbol <- "SPY"
start_date <- "2007-01-31"
end_date <- "2022-12-31"

spy_data <- tq_get(symbol, from = start_date, to = end_date)

spy_monthly_returns <- spy_data %>%
  tq_transmute(select = adjusted, 
               mutate_fun = periodReturn, 
               period = "monthly", 
               type = "log") %>% 
  mutate(SPY.RETURNS = monthly.returns)

rf_symbol <- "DGS3MO"

start_date <- "2007-01-31"
end_date <- "2022-12-30"

rf_data <- tq_get(rf_symbol, from = start_date, to = end_date, get = "economic.data")

rf_monthly <- rf_data %>%
  mutate(date = as.Date(date)) %>%
  group_by(year = format(date, "%Y"), month = format(date, "%m")) %>%
  slice_tail(n = 1) %>%  
  ungroup() %>%
  select(date, price) %>%
  rename(rf.rate = price)

rf_monthly <- rf_monthly %>%
  mutate(rf.rate = (rf.rate / 100) / 12)

```{r}

BenchIVOL_df <- read.csv("https://raw.githubusercontent.com/boykowealth/TailRiskPremium_PortfolioConcept/refs/heads/main/Portfolios_Formed_on_RESVAR.csv")

Merge

slide14_data <- slide14_data %>% mutate(date = as.Date(DATE))
spy_monthly_returns <- spy_monthly_returns %>% mutate(date = as.Date(date))
rf_monthly <- rf_monthly %>% mutate(date = as.Date(date))

slide14_selected <- slide14_data %>% select(date, New, Base)
spy_selected <- spy_monthly_returns %>% select(date, SPY.RETURNS)
rf_selected <- rf_monthly %>% select(date, rf.rate)

slide23_data <- slide14_selected %>%
  left_join(spy_selected, by = "date") %>%
  left_join(rf_selected, by = "date")

slide23_data <- slide23_data %>% 
  summarise(
    across(c(New, Base,SPY.RETURNS, rf.rate ), list(
      Mean = ~ mean(.x, na.rm = TRUE),
      StDev = ~ sd(.x, na.rm = TRUE),
      Max = ~ max(.x, na.rm = TRUE),
      Obs = ~ sum(!is.na(.x)),
      TStat = ~ mean(.x, na.rm = TRUE) / (sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))),
      Sharpe = ~ mean(.x, na.rm = TRUE) / sd(.x, na.rm = TRUE)
    )),
    Correlation = cor(Base, New, use = "complete.obs")
  )

summary_table_23 <- slide23_data %>%
  pivot_longer(everything(), names_to = c("Column", "Metric"), names_sep = "_", values_to = "Value") %>%
  pivot_wider(names_from = Column, values_from = Value)

summary_table_23 %>% 
   gt() %>% 
  fmt_percent(
    columns = where(is.numeric), 
    rows = Metric %in% c("Mean", "StDev", "Max", "Correlation"), 
    decimals = 2
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Sharpe", "TStat"), 
    decimals = 3 
  ) %>% 
  fmt_number(
    columns = where(is.numeric), 
    rows = Metric %in% c("Obs"), 
    decimals = 0 
  )
